%This is to be the abstract...


In today's mining industry, most of the sensor measurements in high temperature environments are expensive and the sensors are not well integrated with the materials treated in the hot temperatures. The conditions can vary much between the sensors location and where the materials are located. 



It is crucial to have high performance measurements to reach a more optimized control over the oven. A more optimized process gives a better combustion which decreases the fuel consumption and is more energy efficient. To increase the performance of these measurements, it is necessary to have wireless sensor systems, which can be well integrated with the materials and have a low cost. This so there is no need to use same system several times and it shouldn't matter if it gets destroyed in the oven.

In this thesis, the focus lies on building the electronics and software for controlling a wide band oxygen sensor. The electronics are built by components with an upper temperature limit of 125 $^\circ$C or above. The sensor itself is supposed to be heated up by an internal heating element. However, in these experiments, it is heated up by the surroundings in the oven.

A major challenge in the work was the design of the control loop to keep the sensor in a correct and stable operating point.

When initial oxygen measurements were compared with reference measurement done simultaneously in the oven, it didn't match well. These differences were shown to be caused by different locations of the sensor and the reference measurements. Further measurements in a live industrial setting confirmed the functionality of the system.

